\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{graphicx}
\usepackage{hyperref}

\newcommand{\R}{\mathbb{R}}
\newcommand{\Cfree}{\mathcal{C}_{\mathrm{free}}}
\newcommand{\Obs}{\mathcal{O}}
\newcommand{\D}{\mathcal{D}}

\title{Dynamic Rotation-Stacked Visibility Graph (DRVG)}
\author{}
\date{}

\begin{document}
\maketitle

\begin{abstract}
\end{abstract}

% ----------------------------------------------------------------------------
% Proof Sketch
% Here we present a rigorous proof of the completeness of our algorithm. We show that as long as the robot 
% is star-shaped with regards to the center, and we have a high enough resolution, our algorithm will always 
% find a solution if one exists. Note that any convex robot is always star-shaped with regards to the center.\\
% We shall prove this in three steps. First, show that the robot can see every configuration it can move to. 
% Second, note that any two rotations in succession is a single rotation. Therefore, the robot will never move 
% two rotations in succession.
% Third, every straight line move will either move to an obstacle vertex, of which there are a globally 
% finite number of, the goal, of which there is only one, or a dynamic vertex. We can show that every move to a 
% dynamic vertex will reveal new area (since it is on a point visibility graph), and thus we will discover the 
% entire environment in a finite number of steps.
% Finally, the visibility graph of entire environment is trivially unique, and we assumed it's completeness.
% ----------------------------------------------------------------------------
\section{Convex Case}
Let \(W\subset \R^2\) be a compact polygonal workspace with finitely many
polygonal obstacles \(\Obs\), and let \(R\) be a polygonal robot whose reference
point \(c\) is its center. Assume that \(R\) is star-shaped with respect to
\(c\). Fix a rotational resolution \(n\) large enough that the corresponding
fully known RVG planner is resolution-complete under its usual clearance
assumptions.

We aim to prove that if a feasible path from \(q_s\) to \(q_g\) exists in the component covered
by the resolution-completeness hypothesis, the online planner returns a feasible
path from \(q_s\) to \(q_g\) after finitely many primitive moves.

Let $R_\theta$ denote the footprint of the robot at orientation $\theta$,
centered at the origin. Since $R$ is star-shaped with respect to its center,
for every $p\in R_\theta$ and every $\lambda\in[0,1]$, we have
$\lambda p\in R_\theta$.

First, consider a collision-free straight translation at fixed orientation
$\theta$, moving the center from $a$ to $b$. For any point $b+p$ of the
final footprint, where $p\in R_\theta$, the segment from $a$ to $b+p$ is
\[
    \gamma(\lambda)
    = a+\lambda(b-a+p)
    = a+\lambda(b-a)+\lambda p,
    \qquad \lambda\in[0,1].
\]
Because $\lambda p\in R_\theta$, the point $\gamma(\lambda)$ lies in the
robot footprint centered at $a+\lambda(b-a)$. Hence the entire segment lies in
the swept volume of the translation. Since the translation is collision-free,
this segment is obstacle-free. Therefore the final footprint is visible from
the current center.

For an in-place rotation, the center is fixed. If the target footprint
$a+R_{\theta'}$ is collision-free, then for every $p\in R_{\theta'}$ and
$\lambda\in[0,1]$,
\[
    a+\lambda p \in a+R_{\theta'} .
\]
Thus every point of the target footprint is visible from the center $a$.
Consequently, every primitive move made by the planner can be certified using
visible free space.

Second, any path may be represented in a normal form with no two consecutive
rotation primitives. Indeed, two consecutive in-place rotations occur about the
same center $a$ and form a single continuous path in the fiber
$\{a\}\times SO(2)$. Replacing their concatenation by one rotation primitive
with the same orientation trace preserves the endpoint, swept set, and
feasibility. Hence it suffices to consider paths that alternate between
translations and rotations.

Third, consider a maximal straight translation in one RVG layer of the currently
discovered free space. In a polygonal visibility graph, such a move can end only
at the goal, at a vertex of a grown obstacle or workspace boundary, or at a
frontier vertex. The first case terminates successfully. The second case can
occur only finitely many times, since the workspace, obstacles, robot, and
resolution $n$ induce only finitely many such graph states, and each state is
expanded at most once by assumption. In the third case, the endpoint is a
dynamic frontier vertex. Since we perform Minkowski sums over the polygonal
visibility graphs, this is equivalent to a point visibility graph, and we will
thus always reveal new area.

After finitely many such moves, either the goal has been found, or no reachable
dynamic frontier vertex remains. Suppose, for contradiction, that some
undiscovered free region in the start component remains reachable. Let
$\tau$ be a feasible path from the discovered region into that undiscovered
region, and let $t^\ast$ be the first parameter at which $\tau$ leaves the
discovered region. Then $\tau(t^\ast)$ lies on a reachable frontier. By
assumption, this frontier induces a reachable dynamic frontier vertex,
contradicting the fact that none remain. Hence the entire reachable component
has been discovered.

Once this component is fully discovered, the online RVG is the same, up to
irrelevant duplicate vertices and tie-breaking choices, as the RVG that would
have been constructed if the environment had been known in advance. Since
$n$ is large enough for the fully known RVG planner to be
resolution-complete, a graph path from $q_s$ to $q_g$ exists whenever a
feasible path exists under the same clearance assumptions. Therefore the online
planner must find and return such a path after finitely many primitive moves.

\bibliographystyle{plain}
\bibliography{references}

\end{document}
